rowing: analysis of sculls in the 2016 Olympics

### 2022-11-22 inst/rowing.Rmd
rowing_table

```{r}
o <- sapply(readLines("rowing.txt"),strsplit," ")
names(o) <- NULL  # names are pointless here
o[1:3]
```

@@

```{r definerowing, cache=TRUE}
rowing <- Reduce("+",sapply(o,race))
summary(rowing)
```

@@

```{r,label=saverowingingdataset}
save(rowing,rowing_minimal,rowing_maxp,rowing_minimal_maxp,file="rowing.rda")
```

>>>>

```{r}
rowing_table <- sapply(readLines("rowing.txt"),strsplit," ")
names(rowing_table) <- NULL  # names are pointless here
rowing_table[1:3]
```

@@

```{r definerowing, cache=TRUE}
rowing <- Reduce("+",sapply(rowing_table,race))
summary(rowing)
```

@@

```{r,label=saverowingingdataset}
save(rowing,rowing_minimal,rowing_maxp,rowing_minimal_maxp,rowing_table,file="rowing.rda")
```
